\bf Faster Neural Machine Translation Inference

### 2018-02-05 fast-beam/fast-beam.tex
fast beam paper

\usepackage[letterpaper]{geometry}
%\usepackage{amta2016}
\usepackage{url}
\usepackage{natbib}
\usepackage{layout}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{argmax}

@@

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Figures~\ref{algo:Add Bias Term} to ~\ref{algo:Find best}.

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE vector $p$, bias vector $b$
\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets p_i + b_i$
\ENDFOR 
\end{algorithmic}
\caption{Add Bias Term}
\label{algo:Add Bias Term}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE vector $p$

\COMMENT{calculate max for softmax stability}

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $max \gets p_i$
  \ENDIF
\ENDFOR

\COMMENT{calculate denominator}

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \STATE $sum \gets sum + \exp(p_i - max)$
\ENDFOR

\COMMENT{calculate softmax}

\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets \frac{\exp(p_i) - max}{sum} $
\ENDFOR

\RETURN $p$

\end{algorithmic}
\caption{Calculate softmax}
\label{algo:Calculate softmax}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE softmax vector $p$

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $max \gets p_i$
    \STATE $best \gets i$
  \ENDIF
\ENDFOR

\RETURN $max$, $best$

\end{algorithmic}
\caption{Find best}
\label{algo:Find best}
\end{figure}

@@

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE vector $p$, bias vector $b$

\COMMENT{add bias, calculate $max$ \& $argmax$}

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i + b_i > max$}
    \STATE $max \gets p_i + b_i$
    \STATE $best \gets i$
  \ENDIF
\ENDFOR

\COMMENT{calculate denominator}

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $sum \gets sum + \exp(p_i - max)$
  \ENDIF
\ENDFOR

\RETURN $\frac{1}{sum}$, $best$

\end{algorithmic}
\caption{Fused softmax and argmax}
\label{algo:Fused Kernel}
\end{figure}

@@

\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\WHILE{more input} 
  \STATE Create batch
  \STATE Encode
  \WHILE{batch is not empty} 
    \STATE Decode batch
    \FOR{each sentence in batch}
      \IF{translation is complete}
        \STATE Remove sentence from batch
      \ENDIF
    \ENDFOR
  \ENDWHILE
\ENDWHILE 
\end{algorithmic}
\caption{Mini-batching}
\label{algo:Mini-batching}
\end{figure}

@@

\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\WHILE{more input} 
  \STATE Create encoding batch
  \STATE Encode
  \STATE Add to queue
\ENDWHILE 
\end{algorithmic}
\caption{Encoding for top-up batching}
\label{algo:Encoding for top-up batching}
\end{figure}

@@

\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE create decoding batch $b$ from queue
\WHILE{$b$ is not empty}
  \STATE Decode $b$
  \STATE Replace completed sentences with new sentence from queue
\ENDWHILE 
\end{algorithmic}
\caption{Decoding for top-up batching}
\label{algo:Decoding for top-up batching}
\end{figure}

>>>>

\usepackage[letterpaper]{geometry}
%\usepackage{amta2016}
\usepackage{url}
\usepackage{natbib}
\usepackage{layout}

\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx

\usepackage{graphicx}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{argmax}

@@

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Figures~\ref{algo:original-softmax-beamsearch}.

\begin{figure} 
\begin{algorithmic}

\Procedure{AddBias}{vector $p$, bias vector $b$}
\ForAll{$p_i$ in $p$}
  \State $p_i \gets p_i + b_i$
\EndFor 
\EndProcedure

\State

\Procedure{Softmax}{vector $p$}

\Comment{calculate max for softmax stability}
\State $max \gets - \infty$ 
\ForAll{$p_i$ in $p$}
  \If{$p_i > max$}
    \State $max \gets p_i$
  \EndIf
\EndFor

\Comment{calculate denominator} 
\State $sum \gets 0$ 
\ForAll{$p_i$ in $p$}
  \State $sum \gets sum + \exp(p_i - max)$
\EndFor

\Comment{calculate softmax}
\ForAll{$p_i$ in $p$}
  \State $p_i \gets \frac{\exp(p_i) - max}{sum} $
\EndFor

\EndProcedure

\State

\Procedure{FindBest}{softmax vector $p$}

\State $max \gets - \infty$ 
\ForAll{$p_i$ in $p$}
  \If{$p_i > max$}
    \State $max \gets p_i$
    \State $best \gets i$
  \EndIf
\EndFor

\EndProcedure

\end{algorithmic}
\caption{Original Softmax and Beam Search Algorithm}
\label{algo:original-softmax-beamsearch}
\end{figure}

@@

% \begin{figure} [h]
% \begin{algorithmic}
% \REQUIRE vector $p$, bias vector $b$
% 
% \COMMENT{add bias, calculate $max$ \& $argmax$}
% 
% \STATE $max \gets - \infty$ 
% \FORALL{$p_i$ in $p$}
%   \IF{$p_i + b_i > max$}
%     \STATE $max \gets p_i + b_i$
%     \STATE $best \gets i$
%   \ENDIF
% \ENDFOR 
% 
% \COMMENT{calculate denominator}
% 
% \STATE $sum \gets 0$ 
% \FORALL{$p_i$ in $p$}
%   \IF{$p_i > max$}
%     \STATE $sum \gets sum + \exp(p_i - max)$
%   \ENDIF
% \ENDFOR 
% 
% \RETURN $\frac{1}{sum}$, $best$ 
% 
% 
% \end{algorithmic}
% \caption{Fused softmax and argmax}
% \label{algo:Fused Kernel}
% \end{figure}

@@

% \begin{figure} [h]
% \begin{algorithmic}
% %\REQUIRE source sentence $s$, translation options
% \WHILE{more input} 
%   \STATE Create batch
%   \STATE Encode
%   \WHILE{batch is not empty} 
%     \STATE Decode batch
%     \FOR{each sentence in batch}
%       \IF{translation is complete}
%         \STATE Remove sentence from batch
%       \ENDIF
%     \ENDFOR
%   \ENDWHILE
% \ENDWHILE 
% \end{algorithmic}
% \caption{Mini-batching}
% \label{algo:Mini-batching}
% \end{figure}

@@

% \begin{figure} [h]
% \begin{algorithmic}
% %\REQUIRE source sentence $s$, translation options
% \WHILE{more input} 
%   \STATE Create encoding batch
%   \STATE Encode
%   \STATE Add to queue
% \ENDWHILE 
% \end{algorithmic}
% \caption{Encoding for top-up batching}
% \label{algo:Encoding for top-up batching}
% \end{figure}

@@

% \begin{figure} [h]
% \begin{algorithmic}
% %\REQUIRE source sentence $s$, translation options
% \STATE create decoding batch $b$ from queue
% \WHILE{$b$ is not empty}
%   \STATE Decode $b$
%   \STATE Replace completed sentences with new sentence from queue
% \ENDWHILE 
% \end{algorithmic}
% \caption{Decoding for top-up batching}
% \label{algo:Decoding for top-up batching}
% \end{figure}
